---
title: "GDC Data"
output: 
  html_notebook:
    code_folding: hide
---

```{r}
library(data.table)
library(reshape2)
library(tidyverse)
```


## analyte_type and analyte_type_id in GDC analytes and aliquots

GDC Data are downloaded from the GDC data portal on 3/1/2021. 

```{r}
# Load the biospecimen data
analytes = read.csv("../data/gdc/biospecimen.cases_selection.2021-03-01/analyte.tsv", sep="\t")
aliquots = read.csv("../data/gdc/biospecimen.cases_selection.2021-03-01/aliquot.tsv", sep="\t")
```


## Analytes

#### analyte_type

```{r}
data.frame(table(analytes$analyte_type))
```

#### analyte_type_id

```{r}
data.frame(table(analytes$analyte_type_id))
```


#### Correlation between the two set of values

```{r}
a_a_tab = data.frame(table(analytes[!(analytes$analyte_type %like% "'" & analytes$analyte_type_id %like% "'"), c('analyte_type_id', 'analyte_type')]))
aa_freq = cbind(ID=rownames(a_a_tab), a_a_tab)
filter(aa_freq, Freq > 0)[, c(2, 3, 4)]
```


## Aliquots

#### analyte_type

```{r}
data.frame(table(aliquots$analyte_type))
```

#### analyte_type_id

```{r}
data.frame(table(aliquots$analyte_type_id))
```

#### Correlation between analyte_type and analyte_type_id values in aliquots

```{r}
a_a_tab = data.frame(table(aliquots[!(aliquots$analyte_type %like% "'" & aliquots$analyte_type_id %like% "'"), c('analyte_type_id', 'analyte_type')]))
aa_freq = cbind(ID=rownames(a_a_tab), a_a_tab)
filter(aa_freq, Freq > 0)[, c(2, 3, 4)]
```


## Diagnosis

```{r}
# Load the biospecimen data
clinical = read.csv("../data/gdc/clinical.cases_selection.2021-03-01/clinical.tsv", sep="\t")
```

#### Correlation between primary_diagnosis and morphology in aliquots

```{r}
clinical.pm_tab = data.frame(table(clinical[!(clinical$primary_diagnosis %like% "'" & clinical$morphology %like% "'"), c('primary_diagnosis', 'morphology')]))
clinical.pm_freq = filter(cbind(ID=rownames(a_a_tab), clinical.pm_tab), Freq > 0)[, c(2,3,4)]
clinical.pm_freq
```

The only morphology code that are grouped with several diagnosis code (ICD-O Morphology Labels) is 9800/3
```{r}
filter(clinical.pm_freq, morphology=='9800/3')
```