---
title: "PDC Data"
output: 
  html_notebook:
    code_folding: hide
---

```{r}
library(data.table)
library(reshape2)
library(tidyverse)
```


## analyte_type and analyte_type_id in GDC analytes and aliquots

GDC Data are downloaded from the GDC data portal on 3/1/2021. 

```{r}
# Load the biospecimen data
pdc.biospecimen = read.csv("../data/pdc/PDC_biospecimen_manifest_03102021_101032.csv")
pdc.studies = read.csv("../data/pdc/PDC_study_manifest_03102021_101016.csv")
```


#### Analyte_type

There's no analyte type in the downloaded data. The analyte type on the web portal appears to be "protein" in most cases manually checked. 

For example, see Aliquot.Submitter.ID: CPT0073530001 in case [C3L-01257](https://proteomic.datacommons.cancer.gov/pdc/case/6e7501ca-118a-11e9-afb9-0a9c39d33490)

```{r}
unique(pdc.biospecimen[, 'Analyte.Type'])
```


## Disease Type

Each data can have more than one disease types, separated by ";". 

No ICD-O based terms are used. All terms appear to be the deprecated GDC terms. 

```{r}
data.frame(table(pdc.studies$Disease.Type))
```